---
title: "Geom, Geom in ggplot2, Which is the Best of Them All?"
format: html
editor: visual
---

# Setup

```{r}
#| label: load-packages
#| message: false

library(tidyverse)
library(openintro)
```

# Part 1 - Visualizing relationships and distributions together

1.  Create a visualization that displays the relationship between two numerical variables (`price` and `area`) as well as the distributions of the individual variables in a single plot.

```{r}
#| label: label-me-1

# add code here
```

2.  Build on the plot from Exercise 1 to show the individual values of the number of beds in houses plotted. Experiment with other aesthetic mappings you can bring in to further improve the display.

```{r}
#| label: label-me-2

# add code here
```

# Part 2 - Visualizing variability

Visualize the mean sale price of houses for each year built along with a measure of the variability of sale prices for that built year. Critique your plots for how appropriately they visualize / communicate the variability in house prices for a given year built.

You're welcomed to use any code developed so far in the slides and build on it.

```{r}
#| label: label-me-3

# add code here
```
